### 2013-04-02 doc/final_report/implementation.tex
Made some changes to design chapter as suggested by Amanda and Maria
Added jqPlot bit

\section{ Web Backend }

@@

\subsection{Database Interaction \& SQLAlchemy}

@@

SQLAlchemy enables the representation of papers, authors and other entities as
Python objects. These objects can also be extended and custom methods added to
them, enabling the creation of specific entity methods such as calculating
CoreSC makeup of papers and computing first, middle and last names from a
single input string of an author's full name.

@@

>>>>

\section{ Web Backend }
\label{sec:backend}

@@

\subsection{Database Interaction \& SQLAlchemy}
\label{sec:dbandsqlalchemy}

@@

SQLAlchemy enables the representation of papers, authors and other entities as
Python objects. These objects can also be extended and custom methods added to
them, enabling the creation of specific entity methods such as calculating
CoreSC makeup of papers and computing first, middle and last names from a
single input string of an author's full name. SQLAlchemy also takes care of
data sanitisation and conversion transparently, making sure that users cannot
input malicious SQL code and storing special characters using relevant text
encoding.

@@

\subsection{ Paper Profile Page }

For the most part, the Paper Profile page was quite simple to implement,
requiring only minimal Javascript and HTML. However, rendering the CoreSC
makeup chart for the paper was less trivial. Rather than rendering the chart
using the server and serving a static image to the user, an interactive
JavaScript chart was generated using jqPlot. jqPlot is a javascript extension
of jQuery designed to help render interactive charts and graphs within a web
browser\cite{jqplot2013}. The CoreSC makeup of the paper is calculated by the
web backend and encoded as JSON in the profile page markup. The jqPlot code is
then called and the CoreSC values read from the page structure, producing an
interactive chart in the user's browser window.

A pie chart was used instead of a bar chart, since it was a more concise and
expressive way of showing the paper's CoreSC makeup within the space available
on the page.
